\section{Conclusions}
Maximum Concurrent Flow has many applications where one needs to route
mulitple commodities simultaneously across a network. Like other
variants of multi-commodity flow, this can be solved exactly using
linear programming methods, but in practice approxmiation algorithms
are often good enough and run much more efficiently. In this paper we
implemented a fully polynomial approximation scheme for solving MCF
first introduced by Garg,
quadratic in both error and the size of the graph (ignoring polylog
factors), when appropriate heuristics are applied. We develop a novel
heuristic that runs theoretically no slower than the original
algorithm, as well as implementing a heuristic that reduces the
algorithm's dependence on the number of commodities.

Our results show that the number of shortest path computations is
quadratic in the error term and is roughly linear in the number of
commodities. The number of shortest path computations in the original
algorithm also appears to be roughly linear in the number of
edges. The technique first proposed by Karakostas to reduce dependence
on $k$ has been shown to make fewer calls to the shortest paths
subroutine than the vanilla implementation, particularly on problem
instances where there is a large number of shared-source
commodities. The two-approximation heuristic was implemented on top of
Karakostas' algorithm, and we observed similar numbers of calls to the
shortest path subroutine, implying that we do not see a dramatic
decrease in runtime in practice from this heuristic, despite the
theoretical benefits. Finally, we observed that our novel heuristic
that did not scale demands unnecessarily outperformed the vanilla
algorithm proposed by Garg in shortest paths computations and wall
time. This leads to hypotheses that we could be sloppier with
demand-scaling at the beginning of our algorithm and carefully
scale-demands as we approach termination to further reduce the number
of phases performed. 

Our codebase can be downloaded from \href{https://github.com/jinpan/6.854-project}{https://github.com/jinpan/6.854-project}. 
